# Code
## Connecting to the DB
```{r}
# Create a connection to SQL Server using ODBC
myconn <- DBI::dbConnect(odbc::odbc(),
          Driver             = "Client Name",
          Server             = "DB Server",
          Database           = "DB Name",
          Trusted_Connection = "Yes"
)

```

## Business Questions
### Which product is the top seller by dollar value?
```{r}
# Writing the query/SELECT statement
top_product_by_dollar_value_query <- 
"SELECT 
	tlg_Product.ProductName,
	sum(tlg_Invoice.AmountOwed) as TotalDollarsSold
FROM tlg_OrderDetail
JOIN tlg_Product ON tlg_OrderDetail.ProductID = tlg_Product.ProductID
JOIN tlg_Invoice ON tlg_OrderDetail.OrderID = tlg_Invoice.OrderID
GROUP BY
	tlg_Product.ProductName
ORDER BY TotalDollarsSold DESC"

# Querying the DB
top_product_by_dollar_value <- dbGetQuery(myconn, top_product_by_dollar_value_query)

# Plotting the data
ggplot(top_product_by_dollar_value) +
  geom_col(aes(y=reorder(ProductName, TotalDollarsSold), x=TotalDollarsSold), col=3) +
  xlab("Total Dollars Sold") +
  ylab("Product Name") +
  ggtitle("Total Dollars Sold by Product") +
  theme_fivethirtyeight()

```

### Which product is the top seller by quantity sold?
```{r}
# Writing the query/SELECT statement
top_product_by_units_sold_query <-
"SELECT
	tlg_Product.ProductName,
	sum(tlg_OrderDetail.Quantity) as QuantitySold
FROM tlg_OrderDetail
JOIN tlg_Product ON tlg_OrderDetail.ProductID = tlg_Product.ProductID
GROUP BY
	tlg_Product.ProductName
ORDER BY QuantitySold DESC"

# Querying the DB
top_product_by_units_sold <- dbGetQuery(myconn, top_product_by_units_sold_query)

# Plotting the data
ggplot(top_product_by_units_sold) +
  geom_col(aes(y=reorder(ProductName, QuantitySold), x=QuantitySold), col=3) +
  xlab("Total Units Sold") +
  ylab("Product Name") +
  ggtitle("Total Units Sold by Product") +
  theme_fivethirtyeight()

```

### How many customers have purchased more than once?
```{r}
# Writing the query/SELECT statement
repeat_customer_distribution_query <-
"SELECT
	A.NumberOfOrders,
	count(A.CustomerID) as NumberOfCustomers
FROM
	(SELECT
		tlg_Order.CustomerID,
		count(tlg_Order.OrderID) as NumberOfOrders
	FROM tlg_Order
	GROUP BY
		tlg_Order.CustomerID) as A
GROUP BY
	A.NumberOfOrders
ORDER BY A.NumberOfOrders"

# Querying the DB
repeat_customer_distribution <- dbGetQuery(myconn, repeat_customer_distribution_query)
repeat_customer_distribution <- repeat_customer_distribution %>% 
  mutate(DistributionOfCustomers = round(NumberOfCustomers / sum(NumberOfCustomers) * 100, 2))

colnames(repeat_customer_distribution) <- c("Number of Orders", "Number of Customers", "Distribution of Customers (%)")

repeat_customer_distribution

```

### What is the distribution of the amount spent by customers in the highest grossing month?
```{r}
# Writing the query/SELECT statement
distribution_of_sales_top_month_query <- 
"SELECT * FROM dbo.tlg_DistributionOfSalesInTopSellingMonth
ORDER BY AmountSpent"

# Querying the DB
distribution_of_sales_top_month <- dbGetQuery(myconn, distribution_of_sales_top_month_query)
distribution_of_sales_top_month <- distribution_of_sales_top_month %>% 
  mutate(DistributionOfCustomers = round(NumberOfCustomers / sum(NumberOfCustomers) * 100, 2)) %>% 
  select(AmountSpent, NumberOfCustomers, DistributionOfCustomers, OrderMonthYear)

colnames(distribution_of_sales_top_month) <- c(
  "Total Amount Spent",
  "Number of Customers",
  "Distribution of Customers (%)",
  "Reference Period (MM-YYYY)"
)

distribution_of_sales_top_month

```

### Which city has the greatest number of customers?
```{r}
# Writing the query/SELECT statement
number_of_customers_by_city_query <-
"SELECT * FROM dbo.tlg_CustomersByCity
ORDER BY NumberOfCustomers DESC"

# Querying the DB
number_of_customers_by_city <- dbGetQuery(myconn, number_of_customers_by_city_query)
number_of_customers_by_city <- number_of_customers_by_city %>% 
  mutate(PercentageOfCustomers = round(NumberOfCustomers / sum(NumberOfCustomers) * 100, 2))

colnames(number_of_customers_by_city) <- c(
  "City",
  "Number of Customers",
  "Percentage of Customers (%)"
)

number_of_customers_by_city

```

### Which employee completes the most orders?
```{r}
# Writing the query/SELECT statement
number_of_orders_closed_by_employee_query <-
"SELECT * FROM dbo.tlg_OrdersClosedByEmployee
ORDER BY NumberOfOrdersClosed DESC"

# Querying the DB
number_of_orders_closed_by_employee <- dbGetQuery(myconn, number_of_orders_closed_by_employee_query)

# Plotting the data
ggplot(number_of_orders_closed_by_employee) +
  geom_col(aes(x=reorder(EmployeeFullName, NumberOfOrdersClosed), y=NumberOfOrdersClosed), fill=2, col=1) +
  xlab("Employee (First name, Last name)") +
  ylab("Number of Orders Closed") +
  ggtitle("Number of Orders Closed by Employee") +
  theme_tufte()


```

## Disconnecting fromt he DB
```{r}
DBI::dbDisconnect(myconn)

```
